Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-15 paper/paper.qmd
update github link and ssrp

---
title: "Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis"
author: "Dingning Li, Yiming Tang, Yingqi Pang"
abstract: "This study replicates and extends previous research on the differential impacts of financial support on microenterprise performance, with a focus on the entrepreneurs' gender. By analyzing data from 3,294 entrepreneurs, we explored the effects of loans, cash grants, and in-kind grants on business ownership, assets, and profitability, while taking personal characteristics into account. Our findings suggest that all forms of financial assistance positively influence microenterprise growth, with in-kind grants being particularly advantageous, especially for female entrepreneurs. This research underscores the importance of tailoring financial interventions to consider gender differences, aiming to promote economic empowerment and enhance microenterprise resilience."
date: February 10, 2024
date-format: long
format: pdf
bibliography: references.bib
toc: true
toc-depth: 3
---
# Introduction

>>>>

---
title: "Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis"
author: "Dingning Li, Yiming Tang, Yingqi Pang"
abstract: "This study replicates and extends previous research on the differential impacts of financial support on microenterprise performance, with a focus on the entrepreneurs' gender. By analyzing data from 3,294 entrepreneurs, we explored the effects of loans, cash grants, and in-kind grants on business ownership, assets, and profitability, while taking personal characteristics into account. Our findings suggest that all forms of financial assistance positively influence microenterprise growth, with in-kind grants being particularly advantageous, especially for female entrepreneurs. This research underscores the importance of tailoring financial interventions to consider gender differences, aiming to promote economic empowerment and enhance microenterprise resilience."
date: February 10, 2024
date-format: long
format: pdf
bibliography: references.bib
toc: true
toc-depth: 3
thanks: "Code and data are available at https://github.com/Yiming1220/Effect-of-Financial-Assistance-on-Business-and-Income-Outcomes.git. Reproduction record available at https://doi.org/10.48152/ssrp-ybfz-kw71"
---
# Introduction
